Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-08-15 paper/paper.tex
feat(paper): Add paragraph to conclusion

>>>>

Despite encountering challenges in packaging the numerous software tools, we were able to observe the adaptability of the Nix package manager and the pleasant user experience that results upon completion of the packaging process.
The results we have obtained indicate that Nix is a suitable solution for replicating identical software environments while simplifying the use and reuse of package definitions for users.
We would love to see more software being packaged for Nix, so that even difficult to install software will be accessible to researchers with ease.
